\texttt{JAXbind}: Bind any function to JAX

### 2024-04-08 paper/paper.tex

To the best of our knowledge no other code currently exists for
connecting generic functions to JAX. The package that comes the closest
is Enzyme-JAX (EnzymeAD, 2024). Enzyme-JAX allows one to differentiate a
C++ function with Enzyme (W. Moses \& Churavy, 2020; W. S. Moses et al.,
2021, 2022) and connect it together with its derivative to JAX. However,
it enforces the use of Enzyme for deriving derivatives and does not
allow for connecting arbitrary code to JAX.

@@

\NormalTok{cotan }\OperatorTok{=}\NormalTok{ (jnp.full((}\DecValTok{4}\NormalTok{,}\DecValTok{3}\NormalTok{), }\FloatTok{6.}\NormalTok{),)}
\NormalTok{res, f\_vjp }\OperatorTok{=}\NormalTok{ jax.vjp(f\_jax, }\OperatorTok{*}\NormalTok{inp)}
\NormalTok{res\_cotan }\OperatorTok{=}\NormalTok{ f\_vjp(cotan)}

@@

\leavevmode\hypertarget{ref-Edenhofer2023NIFTyRE}{}%
Edenhofer, G., Frank, P., Roth, J., Leike, R. H., Guerdi, M.,
Scheel-Platz, L. I., Guardiani, M., Eberle, V., Westerkamp, M., \&
Enßlin, T. A. (2024). \emph{{Re-Envisioning Numerical Information Field
Theory (NIFTy.re): A Library for Gaussian Processes and Variational
Inference}}. \url{http://arxiv.org/abs/2402.16683}

@@

\leavevmode\hypertarget{ref-Moses2022}{}%
Moses, W. S., Narayanan, S. H. K., Paehler, L., Churavy, V., Schanen,
M., Hückelheim, J., Doerfert, J., \& Hovland, P. (2022). Scalable
automatic differentiation of multiple parallel paradigms through
compiler augmentation. \emph{Proceedings of the International Conference
on High Performance Computing, Networking, Storage and Analysis}.
ISBN:~\href{https://worldcat.org/isbn/9784665454445}{9784665454445}

>>>>

The functionality of \texttt{JAXbind} extends the external callback
functionality in JAX. Currently, \texttt{JAXbind}, akin to the external
callback functions in JAX, briefly requires python's global interpreter
lock (GIL) to call the user specified python function. In contrast to
JAX's external callback functions, it allows for both a custom
Jacobian-vector product and vector-Jacobian product. To the best of our
knowledge no other code currently exists for connecting generic
functions and both of their Jacobian products to JAX. The package that
comes the closest is Enzyme-JAX (EnzymeAD, 2024). Enzyme-JAX allows one
to differentiate a C++ function with Enzyme (W. Moses \& Churavy, 2020;
W. S. Moses et al., 2021, 2022) and connect it together with its
derivative to JAX. However, it enforces the use of Enzyme for deriving
derivatives and does not allow for connecting arbitrary code to JAX.

@@

\NormalTok{cotan }\OperatorTok{=}\NormalTok{ [jnp.full((}\DecValTok{4}\NormalTok{,}\DecValTok{3}\NormalTok{), }\FloatTok{6.}\NormalTok{)]}
\NormalTok{res, f\_vjp }\OperatorTok{=}\NormalTok{ jax.vjp(f\_jax, }\OperatorTok{*}\NormalTok{inp)}
\NormalTok{res\_cotan }\OperatorTok{=}\NormalTok{ f\_vjp(cotan)}

@@

\leavevmode\hypertarget{ref-Edenhofer2023NIFTyRE}{}%
Edenhofer, G., Frank, P., Roth, J., Leike, R. H., Guerdi, M.,
Scheel-Platz, L. I., Guardiani, M., Eberle, V., Westerkamp, M., \&
Enßlin, T. A. (2024). \emph{{Re-Envisioning Numerical Information Field
Theory (NIFTy.re): A Library for Gaussian Processes and Variational
Inference}}. \url{https://doi.org/10.48550/arXiv.2402.16683}

@@

\leavevmode\hypertarget{ref-Moses2022}{}%
Moses, W. S., Narayanan, S. H. K., Paehler, L., Churavy, V., Schanen,
M., Hückelheim, J., Doerfert, J., \& Hovland, P. (2022). Scalable
automatic differentiation of multiple parallel paradigms through
compiler augmentation. \emph{Proceedings of the International Conference
on High Performance Computing, Networking, Storage and Analysis}.
\url{https://doi.org/10.1109/SC41404.2022.00065}
